Winter weather on exam dates and matriculation for a prestigious university in Japan

### 2021-04-07 Writeups/paper.tex
Revision done

This study analyzes the effect of winter weathers on exam outcomes in Japan.
For admission, most public universities in Japan require high school seniors and graduates to take a centralized test, called National Center Test for University Admission (Center Test henceforth).
Students take the exam on the same dates in mid-January in their prefectures.\footnote{
  There are 47 prefectures in Japan.
}
This creates a variation in weathers to which they are exposed on the exam dates.

@@

I use two sets of data: weather and matriculation for UTokyo.
For weather information, I obtain data from \Citeauthor{jma}.
Their website maintains the past weather across Japan.
Based on hourly weather on exam dates at prefecture capitals, I use average weather between 6 AM to 6 PM.
Prefecture capitals tend to be most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located at prefecture capitals.
%\footnote{
%  According to inter-edu, \url{https://www.inter-edu.com/univ/2019/jisseki/todai/ranking/}
%}

For matriculation information for UTokyo, I use University Basic Information by \Citeauthor{univ_info}.
This data contains information from 2012 to 2020 on the number of matriculated students for each university by prefectures at which their high schools are located.
I calculate the matriculation shares of each prefecture as the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.\footnote{
  Ideally, the information on admission rather than matriculation should be used since matriculation depends on exam scores and the decision to go to the university or not.
  Due to the lack of information on the number of admitted students by prefecture, I use the information on matriculation.
  For UTokyo, the number of admissions and the number of matriculations are very close:
  In 2020, among 3,083 admitted students, 3,064 students matriculated at UTokyo.
  %Moreover, it is unlikely that weathers on exam dates affect decisions of admitted students to matriculate or not.
}

@@

One potential problem in the analysis is that a student from a high school in a prefecture does not necessarily take Center Test in the same municipality.
This means that, for these students, the weather at the exam sites is measured with errors.
The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get into any university for the first year and retake Center Test next year in his home prefecture.
%\footnote{
%  In 2020, less than 40\% of the admitted students are high-school graduates.
%  In the same year, according to the School Basic Survey, the share of high-school students from junior high schools in different prefectures was 3.9\% \citep{eStat}.
%  If I assume that that this number corresponds to the share of high-school students whose hometowns are in different prefectures, I obtain a rough estimate of the share of the high-school graduates whose high schools and hometowns are in different prefectures as $0.40 * 0.039 = 1.6\%$. 
%}
I consider that, conditional on prefecture fixed effects, the measurement error is likely to be uncorrelated with the error term.
Hence, this classical measurement error can make the estimates conservative.
Another potential concern is that, as discussed in footnote \ref{footnote:prefecture}, students in several municipalities in a prefecture could take Center Test in a neighboring prefecture.
Since neighboring prefectures are geographically close, I consider that the effect of this measurement error on estimates is not large.

@@

In Table \ref{tab:reg_pre10}, the coefficients on snowfall and cumulated snow on the ground are statistically significant.
Combined with the finding in Table \ref{tab:main_reg} that cumulated snow on the ground on the exam dates decreases students' performance, two potential explanations can be given:
(i) snow before the exams can adversely affect students' preparation, and
(ii) snowfall before the exams cumulates snow on the grdound and students' performance is affected by the cumulated snow on the exam dates.
Due to high collinearity of cumulated snow on the exam dates and 10 days before the exams, I cannot identify which mechanism is dominant.

@@

The results show both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam dates.
Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage point, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
Moreover, having more than 10cm of snow on the ground decreases the share by 0.13 percentage point.

>>>>

This study analyzes the effect of winter weather on exam outcomes in Japan.
For admission, most public universities in Japan require high school seniors and graduates to take a centralized test, called National Center Test for University Admission (Center Test henceforth).
Students take the exam on the same dates in mid-January in their prefectures.\footnote{
  There are 47 prefectures in Japan.
}
This creates a variation in weathers to which they are exposed on the exam dates.

@@

I use two sets of data: weather and matriculation for UTokyo.
For weather information, I obtain data from \Citeauthor{jma}.
Their website maintains the past weather across Japan.
Based on hourly weather on exam dates at prefecture capitals, I use average weather between 6 AM to 6 PM.
Prefecture capitals tend to be most populated in each prefecture, and highly-ranked high schools from which many students go to UTokyo are likely to be located at prefecture capitals.

For matriculation information for UTokyo, I use University Basic Information by \Citeauthor{univ_info}.
This data contains information from 2012 to 2020 on the number of matriculated students for each university by prefectures at which their high schools are located.
I calculate the matriculation shares of each prefecture as the ratio of the number of matriculated students from a prefecture to the number of all matriculated students.\footnote{
  %Ideally, the information on admission rather than matriculation should be used since matriculation depends on exam scores and the decision to go to the university or not.
  Due to the lack of information on the number of admitted students by prefecture, I use the information on matriculation.
  For UTokyo, the number of admissions and the number of matriculations are very close:
  In 2020, among 3,083 admitted students, 3,064 students matriculated at UTokyo.
  %Moreover, it is unlikely that weathers on exam dates affect decisions of admitted students to matriculate or not.
}

@@

One potential problem in the analysis is that a student from a high school in a prefecture does not necessarily take Center Test in the same municipality.
This means that, for these students, the weather at the exam sites is measured with errors.
The primary reason for this to happen is that a senior student at a high school located at a prefecture different from his home prefecture fails to get into any university for the first year and retake Center Test next year in his home prefecture.
%\footnote{
%  In 2020, less than 40\% of the admitted students are high-school graduates.
%  In the same year, according to the School Basic Survey, the share of high-school students from junior high schools in different prefectures was 3.9\% \citep{eStat}.
%  If I assume that that this number corresponds to the share of high-school students whose hometowns are in different prefectures, I obtain a rough estimate of the share of the high-school graduates whose high schools and hometowns are in different prefectures as $0.40 * 0.039 = 1.6\%$. 
%}
I consider that, conditional on prefecture fixed effects, the measurement error is likely to be uncorrelated with the error term.
Hence, this classical measurement error can make the estimates conservative.
Another potential concern is that, as discussed in footnote \ref{footnote:prefecture}, students in several municipalities in a prefecture could take Center Test in a neighboring prefecture.
Since neighboring prefectures are geographically close, I consider that this measurement error is not large.

@@

In Table \ref{tab:reg_pre10}, the coefficients on snowfall and cumulated snow on the ground are statistically significant.
Combined with the finding in Table \ref{tab:main_reg} that cumulated snow on the ground on the exam dates decreases students' performance, two potential explanations can be given:
(i) snow before the exams can adversely affect students' preparation, and
(ii) snowfall before the exams cumulates snow on the ground and students' performance is affected by the cumulated snow on the exam dates.
Due to the high correlation of cumulated snow on the exam dates and 10 days before the exams, I cannot identify which mechanism is dominant.

@@

The results show both economically and statistically significant impacts of low temperature and cumulated snow on the ground on the exam dates.
Changing the temperature from 3-6 $^o$C to below 0 $^o$C decreases the matriculation share of a prefecture by 0.18 percentage point, which is 9\% of the mean matriculation share, or 22\% of the median matriculation share.
Moreover, having more than 10cm of snow on the ground decreases the share by 0.11 percentage point.
